Models

### 2021-08-20 analysis/05_model_metrics.Rmd
Clean up

get_model(data = model_data, metric_name = "SES_FRic", "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)", model_id = "base")
```

@@

re_slopes <- pmap_dfr(model_df, get_study_slopes)

study_slopes <- re_slopes %>% 
  filter(model_id == "base") %>%
  rename(study_id = level)

@@

study_slope_data <- study_slopes %>%
  select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              select(-rarefyid) %>% 
              distinct() %>%
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% select(study_id, startyear, duration) %>% distinct())

taxa_slope <- study_slope_data %>%
  mutate(taxa = as.factor(taxa)) %>%
  group_nest(metric) %>%
  mutate(#year_center = map(data, ~scale(.x$year)),
         model = map(data, ~lmer(estimate ~ (1|study_id) + year_scaled + (year_scaled|study_id/rarefyID), 
                                 data = .x)),
           # null_model = map(data, ~lmer(value ~ (year_scaled|study_id/rarefyID), 
           #                       data = .x)),
           # test = map2(model, null_model, anova),
           # test_res = map(test, tidy),
           coef = map(model, tidy),
           ) %>% 
  select(metric, model, coef) %>%
  unnest(cols = c(coef)) %>%
  filter(term == "year_scaled") %>%
  select(-c(effect, group, term, statistic))

#taxa model
taxa_slope <- study_slope_data %>%
  mutate(taxa = as.factor(taxa)) %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(model = map(data, ~glm(estimate ~ taxa, 
                                 data = .x)),
           tukey_mod = map(model, ~glht(., mcp(taxa="Tukey"))),
         tukey_coef = map(tukey_mod, tidy)) %>% 
  select(metric, tukey_coef) %>%
  unnest(cols = c(tukey_coef)) %>%
  rename(covariate = term)

climate_slope <- study_slope_data %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(#year_center = map(data, ~scale(.x$year)),
         #model = map(data, ~lmer(estimate ~ taxa + (1|taxa), 
         model = map(data, ~glm(estimate ~ climate, 
                                 data = .x)),
           tukey_mod = map(model, ~glht(., mcp(climate="Tukey"))),
         tukey_coef = map(tukey_mod, tidy)) %>% 
  select(metric, tukey_coef) %>%
  unnest(cols = c(tukey_coef)) %>%
  rename(covariate = term)

realm_slope <- study_slope_data %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(#year_center = map(data, ~scale(.x$year)),
         #model = map(data, ~lmer(estimate ~ taxa + (1|taxa), 
         model = map(data, ~glm(estimate ~ realm, 
                                 data = .x)),
           tukey_mod = map(model, ~glht(., mcp(realm="Tukey"))),
         tukey_coef = map(tukey_mod, tidy)) %>% 
  select(metric, tukey_coef) %>%
  unnest(cols = c(tukey_coef)) %>%
  rename(covariate = term)

duration_slope <- study_slope_data %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(#year_center = map(data, ~scale(.x$year)),
         #model = map(data, ~lmer(estimate ~ taxa + (1|taxa), 
         model = map(data, ~glm(estimate ~ duration, 
                                 data = .x)),
           coef = map(model, tidy),
           ) %>% 
  select(metric, coef) %>%
  unnest(cols = c(coef)) %>%
  mutate(covariate = "duration")

startyear_slope <- study_slope_data %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(#year_center = map(data, ~scale(.x$year)),
         #model = map(data, ~lmer(estimate ~ taxa + (1|taxa), 
         model = map(data, ~glm(estimate ~ startyear, 
                                 data = .x)),
           coef = map(model, tidy),
           ) %>% 
  select(metric, coef) %>%
  unnest(cols = c(coef)) %>%
  mutate(covariate = "startyear")

#All model estimates in one dataframe
slope_models <- bind_rows(taxa_slope, realm_slope, climate_slope, duration_slope, startyear_slope)

>>>>

#get_model(data = model_data, metric_name = "SES_FRic", "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)", model_id = "base")
```

@@

#get study level slopes for base, and levels for categorical random effect in non-base models
re_slopes <- pmap_dfr(model_df, get_study_slopes)

#get only study-level slopes for the base models
study_slopes <- re_slopes %>% 
  filter(model_id == "base") %>%
  rename(study_id = level)

@@

study_slope_data <- study_slopes %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              dplyr::select(-rarefyid) %>% 
              distinct() %>%
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% dplyr::select(study_id, startyear, duration) %>% distinct())

duration_slope <- study_slope_data %>%
  group_nest(metric) %>%
  mutate(model = map(data, ~glm(estimate ~ duration, 
                                 data = .x)),
           coef = map(model, tidy),
           ) %>% 
  dplyr::select(metric, coef) %>%
  unnest(cols = c(coef)) %>%
  mutate(covariate = "duration")

startyear_slope <- study_slope_data %>%
  group_nest(metric) %>%
  mutate(model = map(data, ~glm(estimate ~ startyear, 
                                 data = .x)),
           coef = map(model, tidy),
           ) %>% 
  dplyr::select(metric, coef) %>%
  unnest(cols = c(coef)) %>%
  mutate(covariate = "startyear")

#All model estimates in one dataframe
slope_models <- bind_rows(duration_slope, startyear_slope)
